Initial environmental impacts of Piney Point wastewater discharge into Tampa Bay, Florida

### 2021-08-13 manu-draft.Rmd
wqtrnds figure added

* Figure \@ref(fig:map) map
* Figure \@ref(fig:timeline) timeline of events
* Figure \@ref(fig:wqmap) map of water quality observations
* Fig 3 Boxplots by week with +/-1sd for monthly long-term, or value median of long-term and monthly for seasonal eval
* Fig 4 seagrass and macroalgae, correlation matrix
* Fig 5 Red tide historic and current, include fish kill reports

@@

>>>>

* Figure \@ref(fig:map) map
* Figure \@ref(fig:timeline) timeline of events
* Figure \@ref(fig:wqmap) map of water quality observations
* Figure \@ref(fig:wqtrnds) boxplots by week with +/-1sd for monthly long-term
* Fig x seagrass and macroalgae, correlation matrix
* Fig x Red tide historic and current, include fish kill reports

@@

```{r wqtrnds, fig.cap = 'Sampled water quality data by week for April to July 2021 in response to wastewater discarge from Piney Point for (a) total nitrogen (mg/L), (b) chlorophyll-a (ug/L), and (c) secchi disk depth (meters).  Observations are aggregated by week and within assessment areas shown in Figure \\@ref(fig:map)a.  Normal ranges for the month of observation (monthly baseline) and area are shown by the blue shaded areas. Normal ranges are defined as within +/-1 standard deviation of the mean for the month of observation from 2006 to 2021 for values collected at long-term monitoring sites within each area.'}
knitr::include_graphics(here('figs/wqtrnds.jpeg'))
```
